Eviction and Crime: Evidence from Boston

### 2023-04-13 writing/paper/main.tex
Updates from Overleaf

    \begin{table}[H]
        \centering
        \input
        \caption{Caption}
        \label{tab:my_label}
    \end{table}

@@

    I select three categories of crime incidents which are more common in

    Second, treatment effects are driven by evictions that were concluded during warm months. Post-treatment impacts of eviction are uniformly smaller in magnitude during cold months and largely insignificant from 0, as shown in Figures 4 and 5. \textcolor{red}{todo!}

    \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_warm_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Warm Months)}
        \label{fig:my_label}
    \end{figure}

       \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_cold_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Cold Months)}
        \label{fig:my_label}
    \end{figure}

    Third, placebo tests using \<crimes that are most common in wealthy areas\> as an outcome do not show evidence

    1. placebo test

    2. warm results

    3. Steady increase

    Point estimates of the post-treatment $ATT(e)$'s become negative and significantly different from zero almost immediately after treatment and remain so for the next three years. Assuming that the units in my sample are vacant for less than three years after eviction, this means that treatment effects are negative both while the property is vacant and once a new tenant arrives.

    This suggests two things about evicted tenants. First, it suggests that just before eviction, they are culprits of, accessories to, or targets of crime incidents.

    Point estimates of the post-treatment ATT remain negative and significantly different from zero not just for the first few months after treatment, but for the first three years after treatment.

    \subsection{Robustness}
    \subsection{How does the lack of execution data bias my results?}

>>>>

    \begin{table}[H]
        \centering
        \input{output/group_0_crimes_500m/tables/placebo_poverty_rates}
        \caption{TODO}
        \label{tab:my_label}
    \end{table}
    \end{landscape}

@@

    \begin{figure}
        \centering
        \includegraphics{output/group_1_crimes_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{TODO}
        \label{fig:my_label}
    \end{figure}

    Third, treatment effects are driven by evictions that were concluded during warm months. Post-treatment impacts of eviction are uniformly smaller in magnitude during cold months and largely insignificant from 0, as shown in Figures 4 and 5. A large body of research has found evidence of significant seasonal increases in crime during warmer months \citep{lauritsen_seasonal_2014}. The fact that treatment effects are largest during warm months is consistent with the hypothesis that evicted tenants interact with crime to a greater extent than the tenants that replace them.

    \begin{figure}[H]
        \centering
        \includegraphics{output/group_0_crimes_cold_500m/figures/att_gt_dr_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Warm Months)}
        \label{fig:my_label}
    \end{figure}

       \begin{figure}[H]
        \centering
        \includegraphics{output/group/figures/att_gt_unconditional_event_study_long_horizon.png}
        \caption{Relationship Between Treatment and Crime Incidents Within 500 Meters (Cases Concluded During Cold Months)}
        \label{fig:my_label}
    \end{figure}

    \subsection{Robustness}
    1. Remove large apartment buildings

    \subsection{How does the lack of execution data bias my results?}
